Msc Thesis Figures

### 2020-08-21 docs/msc_thesis_figures.Rmd
remove clustering
updates, should make rmd lighter

@@

We prepare the data for ordination, and plot the results.

@@

Clustering for land use change transitions

@@

trans_dendro <- as.dendrogram(trans_clust)
trans_memberships <- cutree(trans_clust,4)
# trans_memberships_names <- c("Urb-Def","AgEx-Def",
#                              "AgEx-DeTree","Urb-DeAg")[trans_memberships]
labels_colors(trans_dendro) <- trans_memberships[trans_clust$order]
plot(trans_dendro)
```

Clustering for land use values

@@

values_dendro <- as.dendrogram(values_clust)
values_memberships <- cutree(values_clust,5)
# values_memberships_names <- c("Forest - Dominant","Forest - Agriculture",
#                               "Agriculture - Dominant"," Urban - MD", 
#                               "Urban - HD")[values_memberships]
labels_colors(values_dendro) <- values_memberships[values_clust$order]
plot(values_dendro)

@@

PCA and map for land use change transitions

@@

# trans_biplot
```
![](../thesis/figures/PCA_trans_profiles.png)

@@

PCA and map for land use values

@@

![](../thesis/figures/PCA_data_profiles.png)
```{r land_use_trends_map_2, message=FALSE,  warning=FALSE, out.width="100%"}

@@

@@

@@

@@

@@

@@

ROC curves from fitting both models, plotting with `patchwork` package.

@@

#### Original

@@

@@

@@

@@

@@

@@

### Maps

@@

@@

![](../thesis/figures/historic_compare_urb.png)
![](../thesis/figures/historic_compare_agex.png)

@@

@@

![](../thesis/figures/scenario_39_compare.png)
![](../thesis/figures/scenario_42_compare.png)
![](../thesis/figures/scenario_45_compare.png)
![](../thesis/figures/scenario_48_compare.png)
![](../thesis/figures/scenario_51_compare.png)

@@

@@

@@

##### Other calculations

>>>>

**This regroups most of the figures in the thesis (appendix figures are not included, except for the ROC resample figures and BAU simulated land use change).**

@@

We prepare the data for ordination and compute clustering (figures not displayed here).

@@

Clustering for land use change transitions.

@@

trans_dendro <- as.dendrogram(trans_clust)
trans_memberships <- cutree(trans_clust,4)
# trans_memberships_names <- c("Urb-Def","AgEx-Def",
#                              "AgEx-DeTree","Urb-DeAg")[trans_memberships]
labels_colors(trans_dendro) <- trans_memberships[trans_clust$order]
#plot(trans_dendro)
```

Clustering for land use values.

@@

values_dendro <- as.dendrogram(values_clust)
values_memberships <- cutree(values_clust,5)
# values_memberships_names <- c("Forest - Dominant","Forest - Agriculture",
#                               "Agriculture - Dominant"," Urban - MD", 
#                               "Urban - HD")[values_memberships]
labels_colors(values_dendro) <- values_memberships[values_clust$order]
#plot(values_dendro)

@@

Ordination of land use data (proportions) for municipalities

@@

# trans_biplot
```

![](../thesis/figures/PCA_trans_profiles.png)

Geographical distribution of the 5 profiles identified.

@@

Ordination of land use transition data for municipalities.

@@

![](../thesis/figures/PCA_data_profiles.png)

Geographical distribution of the 4 change profiles identified

```{r land_use_trends_map_2, message=FALSE,  warning=FALSE, out.width="100%"}

@@

Change in mean flow (in \% of the the 1990 flow) between 1990 and 2010, contrasting observed historic change (1990-2010) and simulated change from historic model run.

@@

Change in mean flow (in \% of the the 2010 flow) between 2010 (observed) and 2100 (predicted), contrasting BAU scenario (solid line) with other land use change scenarios - linear graph.

@@

Change in mean flow (in \% of the the 2010 flow) between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other land use change scenarios - radar graph.

@@

Change in mean flow (in \% of the the 2010 flow) between 2010 (observed) and 2100 (predicted), contrasting BAU scenario (solid line) with other conservation scenarios - linear graph.

@@

Change in mean flow (in \% of the the 2010 flow) between 2010 (observed) and 2100 (predicted), contrasting BAU scenario (solid line) with other conservation scenarios - radar graph.

@@

ROC curves from fitting both models, plotted with the `patchwork` package.

@@

Histograms of flow values for the year 2010 comparing the historic model run (1990-2010) with observations.

@@

Histograms of flow values for all species and scenarios, for 2010 (observed) and 2100 (predicted).

@@

Change in the number of features (in \% of the the 2010 flow) identified by the SURF analyssis between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other land use change scenarios - linear graph.

@@

Change in the number of features (in \% of the the 2010 flow) identified by the SURF analyssis between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other land use change scenarios - radar graph.

@@

Change in the number of features (in \% of the the 2010 flow) identified by the SURF analyssis between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other conservation scenarios - linear graph.

@@

Change in the number of features (in \% of the the 2010 flow) identified by the SURF analyssis between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other conservation scenarios - radar graph.

@@

### Prediction maps

@@

Predicted probability of urbanization (left) vs observed urbanization (right) between 1990 and 2010.

@@

![](../thesis/figures/historic_compare_urb.png)

Predicted probability of agricultural expansion (left) vs observed agricultural expansion (right) between 1990 and 2010.

![](../thesis/figures/historic_compare_agex.png)

@@

Land use maps showing predictions of land use changes (Only BAU is displayed below).

@@

Comparison of Monteregie at the beginning of the BAU scenario in 2010, and at the end in 2100 (under baseline climate scenario).

![](../thesis/figures/scenario_39_compare.png)
<!--
![](../thesis/figures/scenario_42_compare.png)
![](../thesis/figures/scenario_45_compare.png)
![](../thesis/figures/scenario_48_compare.png)
![](../thesis/figures/scenario_51_compare.png)
-->

@@

Land use class frequencies in 2010 (observed) and 2100 (predicted) for the BAU and Reforestation scenarios (under baseline climate scenario).

@@

Land use class frequencies in 2010 (observed) and 2100 (predicted) for the BAU and conservation scenarios (under baseline climate scenario).

@@

##### Other code for calculation
